Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Change all occurences of quality to time-to-close wherever needed

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

The answers to our research questions are all statistically significant and they can summarised as follows:
\begin{itemize}
  \item having attachments improves the quality of a ticket;
  \item having steps to reproduce improves the quality of a ticket;
  \item having stack traces improves the quality of a ticket;
  \item more grammar errors imply lower ticket quality;
  \item lower sentiment scores result in lower ticket quality;
  \item verbose comments result in lower ticket quality;
  \item verbose summary and description imply lower ticket quality.
\end{itemize}

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
as the number of comments increases, the quality of the ticket decreases.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets.

@@

On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
each other for doing a great job.

@@

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce reduces the time-to-close for a ticket;
  \item the presence of stack traces reduces the time-to-close for a ticket;
  \item the presence of attachments reduces the time-to-close for a ticket - more specifically tickets with screenshots, 
  config files or text files help tickets get closed quicker than those without attachments;
  \item higher numbers of grammar errors imply increased time-to-close values;
  \item higher sentiment scores imply reduced time-to-close values for a ticket;
  \item higher numbers of words in comments imply increased time-to-close values for a ticket;
  \item higher number of words in description and summary increase the time-to-close values for tickets.
\end{itemize}

>>>>

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence time-to-close the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

The answers to our research questions are all statistically significant and they can summarised as follows:
\begin{itemize}
  \item having attachments reduces time-to-close of a ticket;
  \item having steps to reproduce reduces time-to-close of a ticket;
  \item having stack traces reduces time-to-close of a ticket;
  \item more grammar errors imply increase time-to-close values;
  \item lower sentiment scores result in increased time-to-close values;
  \item verbose comments result in increased time-to-close values;
  \item verbose summary and description imply increased time-to-close values.
\end{itemize}

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
as the number of comments increases, the time-to-close value of the ticket also increases.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets (i.e. increased time-to-close).

@@

On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
each other for doing a great job.

@@

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the time-to-close value of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce reduces the time-to-close for a ticket;
  \item the presence of stack traces reduces the time-to-close for a ticket;
  \item the presence of attachments reduces the time-to-close for a ticket - more specifically tickets with screenshots, 
  config files or text files help tickets get closed quicker than those without attachments;
  \item higher numbers of grammar errors imply increased time-to-close values;
  \item higher sentiment scores imply reduced time-to-close values for a ticket;
  \item higher numbers of words in comments imply increased time-to-close values for a ticket;
  \item higher number of words in description and summary increase the time-to-close values for tickets.
\end{itemize}
